#MSDS Spring 2018 
##DATA 607 Data Aquisition and Management
####Jiadi Li
####Week 3 Assignment:R Character Manipulation and Date Processing

Chapter 8
3.Copy the introductory example. The vector name stores the extracted names.
```{r}
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

library(stringr)
name <- unlist(str_extract_all(raw.data,"[[:alpha:]., ]{2,}"))
name
```

(a) Use the tools of this chapter to rearrange the vector so that all elements conform to the standard first_name last_name.
```{r}
for (i in 1:length(name)) {
  if (str_detect(name[i],",")) {
    name_replace <- unlist(str_split(name[i],","))
    name[i] <- str_c(name_replace[2]," ",name_replace[1])
  }
}
name
```

(b) Construct a logical vector indicating whether a character has a title (i.e.,Rev. and Dr.).
```{r}
title_list <- unlist(str_extract_all(name,"^[:alpha:]{2,}\\. "))
str_detect(name,title_list)
```

(c) Construct a logical vector indicating whether a character has a second name.
```{r}
second_name <- unlist(str_extract_all(name,"[:print:]? [:alpha:]\\. "))
str_detect(name,second_name)
```

4.Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.<br/>
(a) [0-9]+\\$  
one or more digits followed by a dollar sign  
```{r}
example_a <- c("37281394$","5$")
str_detect(example_a,"[0-9]+\\$")
```

(b) \\b[a-z]{1,4}\\b  
one to four lower case letters only with nothing at the front or back
```{r}
example_b <- c("agd","enjs")
str_detect(example_b,"\\b[a-z]{1,4}\\b")
```

(c) .*?\\.txt$  
any number of any character followed by ".txt"
```{r}
example_c <- c("dswer.txt","e.txt",".txt")
str_detect(example_c,".*?\\.txt$")
```

(d) \\d{2}/\\d{2}/\\d{4}  
two digits followed by "/" followed by two digits followed by "/" followed by four digits. Normally used to show dates.
```{r}
example_d <- c("02/18/2018","10/15/1993")
str_detect(example_d,"\\d{2}/\\d{2}/\\d{4}")
```

(e) <(.+?)>.+?</\\1>  
any number of character within "< >" followed by any number of any character followed by any character (exactly same as the first group of character in < >) within "</>" 
```{r}
example_e <- c("<hello>world</hello>")
str_detect(example_e,"<(.+?)>.+?</\\1>")
```

9.The following code hides a secret message. Crack it with R and regular expressions.
Hint: Some of the characters are more revealing than others! The code snippet is also available in the materials at www.r-datacollection.com.

```{r}
raw.data <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
code <- str_replace_all(str_replace_all(raw.data,"[:lower:]?[:digit:]?",""),"\\."," ")
code
```